Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-01-26 paper/main.tex
Fixed latex markup errors that were preventing build.

In this section, we present __ sets of experiment to benchmark the performance of the PALM algorithm on CPU and GPU platforms. To generate a meaningful comparison between different hardware architectures, we compare on a per-board basis:  For CPU implementations, the benchmark makes use of as all of the cores in as many cpu's are present.  For GPU implementations, the benchmark makes the best use of the entire GPU chip (most GPU boards have a single GPU chip). Both implementations utilized single precision floating point datatypes and were verified to output results differing by no more than 10^-4.

To construct the benchmark for synthetic data, we first created an mxn matrix A with entries \+- 1 each with a 50\% chance.  Then we created a sparse vector x0 with k\% nonzero random entries.  We also created a sparse vector yk with the same number of non-zero entries as x.  Let y0 = A*x0 + yk.  We timed the time taken for the ALM algorithm using y0, A, and other inputs.  The other inputs included, maximum number of inner/outer loop iterations, and inner/outer loop tolerance level.
% give a discusison of how to construct the benchmark:
% one paragraph for protocol on how to construct synthetic data
% second P for protocol on how to construct the face data

>>>>

In this section, we present INSERTNUMBERHERE sets of experiment to benchmark the performance
of the PALM algorithm on CPU and GPU platforms. To generate a meaningful
comparison between different hardware architectures, we compare on a per-board
basis:  For CPU implementations, the benchmark makes use of as all of the cores
in as many cpu's are present.  For GPU implementations, the benchmark makes the
best use of the entire GPU chip (most GPU boards have a single GPU chip). Both
implementations utilized single precision floating point datatypes and were
verified to output results differing by no more than $10^{-4}$.

To construct the benchmark for synthetic data, we first created an $m \times n$
matrix $A$ with entries $\pm 1$ each with a $50\%$ chance.  Then we created a
sparse vector $\x_0$ with $k\%$ nonzero random entries.  We also created a
sparse vector $y_k$ with the same number of non-zero entries as $\x$.  Let
$\y_0 = A \x_0 + \y_k$.  We timed the time taken for the ALM algorithm using
$\y_0$, $A$, and other inputs.  The other inputs included, maximum number of
inner/outer loop iterations, and inner/outer loop tolerance level.
% give a discusison of how to construct the benchmark: one paragraph for
% protocol on how to construct synthetic data second P for protocol on how to
% construct the face data
